\documentclass[12pt]{article}
\begin{document}
\title{'Lost in Code' }
\author{C. Sgro / A. Mamyshev / M. Segar / N. Alkaydi}
\maketitle

\paragraph*{}
The goal is to make a text based story line driven RPG / Adventure with quiz like elements. 

\section{Basic Script}


\section{Basic Gameplay Elements}
\begin{enumerate}
\item Virtual world concept.
\item The protagonist is looking for a way to get out this world. Traveling throughout the world and coming across certain puzzles (and successfully solving them) contributes to that goal. 
\item Ability to pick certain side quests to gain gold which can be consequently used to buy  certain items that can be used to simplify problem solving, slow down the rate at which player parameters drop as well as restore those said parameters. ( aka 'potions' in a typical fantasy based RPG game)
\item After solving a number of puzzles, the player comes across enemies ( aka 'functions'). Ideally they should be un-skippable unless the player is in possession of a certain item. To kill them, player has to crack their code. Every time the player kills one of those characters their code mutates. Incorrectly cracked enemy drains player's health. (\textit{ look below})
\item In general, every incorrectly answered question should drain player's Stamina. Stamina 'potions' can be found randomly throughout the world. Similarly, every correctly answered question should add to player's Intelligence parameter.  Ideally,  Intelligence  parameter should affect the complexity of puzzles, whereas Stamina should affect the like hood of finding certain useful items in the world.
\item Ability to talk to certain characters and receive certain assistance from them. 
\item Player-related parameters. 
\begin{itemize}
\item Stamina - every incorrectly answered question will decrease stamina.
\item Intelligence - every correctly answered question will increase stamina.
\item Health - rather self explanatory. 
\end{itemize}


\end{enumerate}  

    


\end{document} 